Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-11-15 paper/main.tex
Added more to the candidate selection section

While the official \ac{NIST} \ac{SHA}-3 second round submissions contain both
a reference version and different optimized versions of the candidates, it does not
appear to be updated since the submission deadline on September 15, 2009. They
also do not contain any benchmarking utility which could be used to decide on
the best implementation for a particular platform or architecture. \ac{SUPERCOP}
on the other hand, provides both, in combination with results stating which
compiler arguments gives the best performance. On the downside, the
\ac{SUPERCOP} \ac{API} only specifies the \texttt{crypto\_hash()} function and
not an \texttt{update()} function which Tahoe-\ac{LAFS} is dependent on using.

@@

The chosen implementations are shown in \ref{tbl:sha3:implementations} and
their compiler flags used, which are extracted from the \ac{SUPERCOP} results
can be seen in \ref{tbl:sha3:compilerflags}. It should be noted that 32 in
blake32 does not refer to the output length of the function, but the fact that
the algorithm is optimized for 32-bit usage. 512 in Keccackc512 also does not
mean 512-bit output, but 512 cycles in the internal function. For the most part
we have found working versions of all candidates in \ac{SUPERCOP}, however
there are some exceptions.

@@

\paragraph{Cubehash} sadly does not have a version in supercop with a 256-bit
ouput, which is why we have only included a version from sphlib.

\input{tables/sha3_implementations}
\input{tables/sha3_flags}

@@

% Maybe cite
% \url{http://tahoe-lafs.org/trac/tahoe-lafs/wiki/Performance?version=32}
What is tested and what is not tested?

>>>>

While the official \ac{NIST} \ac{SHA}-3 second round submissions contain both
a reference version and optimized versions of the candidates, it does not
appear to be updated since the submission deadline on September 15, 2009. They
also do not contain any benchmarking utility which could be used to decide on
the best implementation for a particular platform or architecture. \ac{SUPERCOP}
on the other hand, provides both, in combination with results stating which
compiler arguments gives the best performance. On the downside, the
\ac{SUPERCOP} \ac{API} only specifies the \texttt{crypto\_hash()} function and
not an \texttt{update()} function which Tahoe-\ac{LAFS} is dependent on using.

@@

\input{tables/sha3_implementations}

The chosen implementations are shown in Table \ref{tbl:sha3:implementations}
and their compiler flags used, which are extracted from the \ac{SUPERCOP}
results can be seen in Table\ref{tbl:sha3:compilerflags}. It should be noted
that 32 in blake32 does not refer to the output length of the function, but the
fact that the algorithm is optimized for 32-bit usage. 512 in Keccackc512 also
does not mean 512-bit output, but 512 cycles in the internal function. The
relative speeds of the implementations chosen compared to the best version in
\ac{SUPERCOP} and relative speed of the benchmark compared to other candidates
can bee seen in Table \ref{tbl:sha3:speedrelative}. For the most part we have
found working versions of all candidates in \ac{SUPERCOP}, however there are
some exceptions.

\input{tables/sha3_flags}

\input{tables/sha3_relativespeed}

@@

\paragraph{Cubehash} sadly does not have a version in \ac{SUPERCOP} with a 256-bit
output, which is why we have only included a version from sphlib.

\paragraph{Simd vect128 implementation} does not by default conform to
criteria 4, because of a bug in the implementation. This has confirmed by the
author who also supplied us with a patch to correct the bug.

\paragraph{Blake32 \ac{SSSE3}} implementation also fail to wholly fulfill
criteria 4, however it does validate all test vectors that have a length 
in bits which is a multiple of 8. Since our python wrappers only allow, and
only need, to provide data in full bytes we decided to keep this
implementation.

@@

% Maybe cite
% \url{http://tahoe-lafs.org/trac/tahoe-lafs/wiki/Performance?version=32}

What is tested and what is not tested?
